Robust and Efficient CSI Compression Using CLLWCsiNet in Noisy MIMO Environments

### 2025-04-15 Revise-version.tex
txs auto checkin

>>>>

Our work assumes Rayleigh fading for the system model but trains on COST 2100 data, which introduces a discrepancy between the idealized channel and the realistic training environment. While this approach provides a tractable baseline, future work should align the system model with geometry-based channel models (e.g., COST 2100 or 3GPP TR 38.901) to fully capture spatial correlations and frequency-dependent effects in end-to-end simulations.
